### 2013-03-28 doc/sosp13/intro.tex

>>>>

As a general design philosophy, \Grappa trades latency for throughput.  By \emph{increasing} latency in key components of the system we are able to: increase effective random access memory bandwidth by delaying and aggregating messages; increase synchronization rate by delegating atomic operations to gatekeeper cores, even when referencing node-local global data; and improve load balance by tolerating the delays incurred when work-stealing.  \Grappa then exploits parallelism to overcome latency.
